Convergence Studies of Mass Transport in Disks with Gravitational Instabilities. \\ I. The Constant Cooling Time Case

### 2011-09-14 Response_to_Referee1.txt

This is the response to the first referee report for ApJ submission MS#ApJ83382

My primary concern with the analysis is the neglect of the Reynolds stress component when calculating the
effective \alpha viscosity. The authors show that as the disk resolution is increased, more power is
transferred into higher m-structures approaching the dissipation scale in the code. It seems likely that the
shift also causes velocity correlations on this scale, which would produce extra angular momentum transport
and thus a higher effective \alpha.

* It should be noted that the measurement presented in Table 1 and Figure 3 of the manuscript are those of the
Fourier amplitudes, as defined in eqns 2 and 3. As can be seen by their definition, these values do not 
directly measure the power in a given eignmode. In addtion, each particular m value makes a relatively minor 
contribution for large m (i.e. m > 20). The measurement of A_m also includes no phase information, so A_m
is *not* necessarily a good indicator of coherent density structures or organized velocity correlations.

@@

pg 9: What does is mean that the surface density approximates 1/r?

*Wording changed to be more clear.

pg 9: The authors use \gamma  = 5/3 for a protostellar disk, which should be \gamma=7/5. It would be useful to
note this as the critical cooling boundary is a function of \gamma.

*Discussion and citations to Boley et al. 2007, who cover this issue in great detail are now included. In fact,
it is not clear what the correct physical choice is for molecular hydrogen when using a fixed \gamma.

### 2011-10-26 Response_to_Referee1.txt

This is the response to the first referee report for ApJ submission MS#ApJ83382

My primary concern with the analysis is the neglect of the Reynolds stress component when calculating the
effective \alpha viscosity. The authors show that as the disk resolution is increased, more power is
transferred into higher m-structures approaching the dissipation scale in the code. It seems likely that the
shift also causes velocity correlations on this scale, which would produce extra angular momentum transport
and thus a higher effective \alpha.

* It should be noted that the measurement presented in Table 1 and Figure 3 of the manuscript are those of the
Fourier amplitudes, as defined in eqns 2 and 3. As can be seen by their definition, these values do not
directly measure the power in a given eignmode. In addtion, each particular m value makes a relatively minor
contribution for large m (i.e. m > 20). The measurement of A_m also includes no phase information, so A_m is
not necessarily a good indicator of coherent density structures or organized velocity correlations.

@@

I do not understand the author's claim that it is too difficult or unreliable to measure Reynolds
stresses. This paper would be greatly improved by showing how the Reynolds term evolves with resolution. In
fact, I wonder whether all or some of the decrease in the transport at higher resolution would disappear if
this latter term were included.

* The difficulty arises from the fact that the Reynolds stress is typically defined as R_ij = rho*u'_i*u'_j
  where u'_i and u'_j are the fluctuations in the velocity field. The fluctuating pieces of the velocity field
  are defined as u'_i = u_i - u<avg>_i, but in a gravitationally unstable disk with extended non-axisymmetric
  spiral structures, the proper definition of u<avg> (particularly in the phi direction) is unclear. We measured the
  Reynolds stresses using several different definitions for u<avg> and obtained results that varied
  dramatically (by an order of magnitude in some cases). The cases we tried were, using an azimuthal average
  for u<avg>_phi and 0 for u<avg>_r, using an average +/- 2 cells in the direction of interest, using an
  equiangular average in the direction of interest (i.e. the number of cells used in the average for the phi
  direction increased with resolution), using a +/- 2 cell patch around the cell, and using an equiangular
  patch. As stated earlier, results for each of these cases varied substantially. It is also not clear what is
  the proper scale to average over, as one would like to measure the Reynolds stress caused by turbulent
  motion, not the ordered motion of spiral arms. SAY SOMETHING HERE ABOUT THE MOST LIKELY CASE BEING A MERE FRACTION OF THE GRAV TORQUE

@@

In addition to measuring the Reynolds stresses directly, the authors could also look at the mass accretion
rate through rings in order to quantify the effective \alpha. The latter would be another way to get at the
contribution from Reynolds stresses.

* We were able to make this measurement and the mass accretion shows a similar trend to the gravitational
  torque. In addition we calculated the predicted mass accretion based on the measured torques (see Boley et
  al. 2006 equation 22). These are roughly in line with the measured mass accretion rates. (See attached
  figures.)

### 2011-11-03 Response_to_Referee1.txt

My primary concern with the analysis is the neglect of the Reynolds stress component when calculating the
effective \alpha viscosity. The authors show that as the disk resolution is increased, more power is
transferred into higher m-structures approaching the dissipation scale in the code. It seems likely that the
shift also causes velocity correlations on this scale, which would produce extra angular momentum transport
and thus a higher effective \alpha.

* It should be noted that the measurement presented in Table 1 and Figure 3 of the manuscript are those of the
Fourier amplitudes, as defined in eqns 2 and 3. As can be seen by their definition, these values do not
directly measure the power in a given eignmode. In addtion, each particular m value makes a relatively minor
contribution for large m (i.e. m > 20). The measurement of A_m also includes no phase information, so A_m is
not necessarily a good indicator of coherent density structures or organized velocity correlations.

I do not understand the author's claim that it is too difficult or unreliable to measure Reynolds
stresses. This paper would be greatly improved by showing how the Reynolds term evolves with resolution. In
fact, I wonder whether all or some of the decrease in the transport at higher resolution would disappear if
this latter term were included.

* The difficulty arises from the fact that the Reynolds stress is typically defined as R_ij = rho*u'_i*u'_j
  where u'_i and u'_j are the fluctuations in the velocity field. The fluctuating pieces of the velocity field
  are defined as u'_i = u_i - u<avg>_i, but in a gravitationally unstable disk with extended non-axisymmetric
  spiral structures, the proper definition of u<avg> (particularly in the phi direction) is unclear. We measured the
  Reynolds stresses using several different definitions for u<avg> and obtained results that varied
  dramatically (by an order of magnitude in some cases). The cases we tried were, using an azimuthal average
  for u<avg>_phi and 0 for u<avg>_r, using an average +/- 2 cells in the direction of interest, using an
  equiangular average in the direction of interest (i.e. the number of cells used in the average for the phi
  direction increased with resolution), using a +/- 2 cell patch around the cell, and using an equiangular
  patch. As stated earlier, results for each of these cases varied substantially. It is also not clear what is
  the proper scale to average over, as one would like to measure the Reynolds stress caused by turbulent
  motion, not the ordered motion of spiral arms. In fact, when the Reynolds stress is measured by using a +/-
  2 cell patch in both directions, the stresses measured are a few percent of the gravitational torques. (See
  attached figures.) response_to_referee1_fig1a.eps shows the measured torques from the Reynolds stress from
  10 to 50 AU averaged from 12 to 18 ORP for  LMAX = 64(black), 128(blue), 256(green), and 512(red), while
  response_to_referee1_fig1b.eps shows the measured gravitational torques averaged over the same time period.

@@

In addition to measuring the Reynolds stresses directly, the authors could also look at the mass accretion
rate through rings in order to quantify the effective \alpha. The latter would be another way to get at the
contribution from Reynolds stresses.

* We were able to make this measurement and the mass accretion shows a similar trend to the gravitational
  torque. In addition we calculated the predicted mass accretion based on the measured torques (see Boley et
  al. 2006 equation 22). These are roughly in line with the measured mass accretion rates. Overall the average
  from 12 to 18 ORP of the absolute value of the measured rates follows the same trend as the torques. For
  LMAX = 64 the average of the absolute value of the rate was 8.9 x 10^-7 m_sun/yr, for LMAX = 128 the average
  of the absolute value of the rate was 3.7 x 10^-7 m_sun/yr, for LMAX = 256 the average of the absolute value
  of the rate was  2.5 x 10^-7 m_sun/yr, and for LMAX = 512 the average of the absolute value of the rate was
  2.4 x 10^-7 m_sun/yr. (See attached figure.) In response_to_referee1_fig2.eps the solid lines show the
  predicted mdots (x10^-6 m_sun/yr) vs. radius (AU) from the measured gravitational torques, while the dashed
  lines show the actual measured mass accretion rates from 12 to 18 ORP. The color scale is the same as in fig1.

### 2011-11-07 Paper_1.tex
Added Mdots to the table and some descriptive text.
	modified:   Paper_1.tex

The initially unstable disk model passed through several phases of evolution \citep[see also][]{pickett2003, mejia2005}.  
During the initial axisymmetric phase, 
which lasts several ORPs, the disk cools and contracts.  The contraction is small radially but dramatic in the vertical direction. Around 3 to 4 ORPs, the instabilities begin to grow to nonlinear amplitudes, and the disk 
then undergoes a strong burst of GIs that predominantly manifest themselves in a few discrete global spiral modes.  The disk expands violently during the burst phase, producing a significant rearrangement of the disk's mass distribution on a timescale of a few ORPs. This is then followed by a period of several ORPs where heating temporarily washes out some of the non-axisymmetry in the disk.  Finally, following this transition phase, the disk settles into a quasi-steady, long-lived asymptotic 
phase of sustained GI-activity over a large part of the disk, with an overall balance of heating and cooling.

Simulations were run with four different angular resolutions, with grid sizes in cylindrical coordinates $(r,\phi,z)$ of  $(j_{max}, k_{max}, l_{max}) =$ (512,64,64), (512,64,128), (512,64,256), and (512,64,512). 
For reference, the radius $r = 33$ AU at which the ORP is defined is at radial cell $j = 200$.  The radial grid extends to 512
to accomodate disk expansion during outburst.
Because of the computational overhead associated with running each simulation starting from $t = 0$, the $l_{max} =$ 128 simulation was run through the axisymmetric, burst and transition phases. Simulations using $l_{max} =$ 64, 256, and 512 all begin by a linear interpolation of the $l_{max} =$ 128 simulation to higher or lower azimuthal resolution at 9.6 ORPs, near the end of the transition
phase. Although this strategy saves a large amount of computational time, it limits the scope of the analysis to the asymptotic phase. By 12 ORPs, all four disks appear to have transitioned to the asymptotic state,
e.g., they all display roughly steady $Q(r)$ profiles starting at $\sim 12$ ORPs.  All simulations were 
run through $\sim 18$ ORPs.

@@

Figure \ref{fig:DensityPlots}, shows mid-plane and radial densities  at $t \sim 18$ ORPs for the $l_{max} =$ 64, 128, 256, and 512 simulations. It is readily apparent that the character of the non-axisymmetric density structures differ with 
resolution. One can clearly see that the lower resolution simulations, i.e., $l_{max} = 64$ and 128, have primarily low-order structures with $m = 2$ and 3 dominating. In contrast, the higher resolution simulations have much more fine structure, 
and the low-order $m$-values no longer dominate.  
The lower resolution (smaller $l_{max}$) simulations display longer wavelength spiral structures, with larger amplitudes and more coherence than those seen in higher resolution simulations. Higher angular resolution allows non-axisymmetric structures to grow in higher-order azimuthal $m$-values, as demonstrated by a Fourier decomposition of the density. The strengths of these components are given by their global Fourier amplitudes,

\begin{equation}
A_m = \frac{(a_m^2 + b_m^2)^{1/2}}{\pi\int\rho_o \varpi {\rm d}\varpi {\rm d}z},
\end{equation}
where
\begin{subequations}
\begin{align}
a_m &= \int \rho \cos(m\phi)\varpi {\rm d}\varpi {\rm d}z {\rm d}\phi,\\
b_m &=\int \rho \sin(m\phi)\varpi {\rm d}\varpi {\rm d}z {\rm d}\phi.
\end{align}
\end{subequations}
Here  $\rho_o$ is the axisymmetric component of the density. In what follows, $A_m$ is averaged over time to suppress fluctuations on the dynamic timescale due to the chaotic nature of GIs in the asymptotic  phase.
In particular, $\langle A_{tot} \rangle$ will represent the power over the radial range 10 -- 40 AU, summed from $ m = 2$ to $l_{max}/2$ and averaged over the time range 12 -- 18 ORPs. The Fourier amplitudes cannot be measured at resolutions smaller than $l_{max}/2$, therefore $A_m$ is limited to modes $m \le l_{max}/2$.  
Because the central star is artificially fixed to the grid center, the $m=1$ mode may not
be accurately treated. For this reason, it is excluded from $\langle A_{tot} \rangle$.  As discussed below in \S3.2,
we expect this exclusion to have minimal impact on the results of this work.

@@

The gravitational stresses of equation \eqref{alpha1} can be evaluated using the gravitational torque of equation \eqref{torque1}, i.e.,
\begin{equation}
\label{newtonstress}
\begin{split}
 T_{\varpi\phi}^{grav}\left( \varpi \right) & = \frac{1}{2\pi\varpi^2}C_Z\\
                                & = - \frac{1}{2\pi\varpi^2} \int \rho\frac{\partial\Phi}{\partial\phi} {\rm d}V.
\end{split}
\end{equation}
Figure \ref{fig:alpha_v_radius} shows $\alpha_{\rm{eff}}$, time-averaged from 12 to 18 ORPs, calculated using equations \eqref{alpha1} and \eqref{newtonstress},
for the four grid resolutions.  For comparison, 
$\alpha_{\rm{eff}}$ predicted by equation \eqref{eq:gammie} from \citet{gammie2001} are plotted for disks.  The lower  Gammie curve applies for the strongly self-gravitating limit while the upper curve 
represents the non-self-gravitating limit.   The $l_{max} = 512$ curve is consistent with these two limits.  However, 
the  $l_{max} = 512$ curve does not represent a converged model.
To determine whether the converged value of $\alpha_{\rm{eff}}$ is consistent with predictions, we examine 
the spatially (10 -- 40 AU) and temporally (12 -- 18 ORP) averaged  $\alpha_{avg}$,
provided in table 1, for each value of  $l_{max}$.    A Richardson extrapolation applied to these values  
converges to $\alpha_{avg} = 0.017$ (over the same radial  and time range)
as the grid spacing goes to zero.   This falls
between the $\alpha_{avg}$ values for the Gammie curves 0.014 (strongly self-gravitating) and 0.027 (non-self-gravitating).

@@

The results above permit an assessment of appropriate azimuthal grids for the
problem under consideration and similar problems. The $l_{max} = 512$ simulation yields a value 
for $\alpha_{avg}$ of 0.020. This overestimates the extrapolated converged value of $\alpha_{avg}
= 0.017$ by $\sim 18$\%. The $l_{max} = 512$ simulation also overestimates the fractional
power in the high-order ($m = 2$ -- 7) modes by essentially the same percentage. However, it should be noted that the fractional difference between successive doubling of the resolution has decreased for $l_{max} = 512$. From $l_{max} =64$ to 128 the fractional difference in $\alpha_{avg}$ is 36\%. This decreases to 26\% for the jump from $l_{max} = 256$ to 512. Furthermore, the converged value represents infinite azimuthal resolution, which is, of course, impossible to achieve in a fixed grid scheme. 
%It is unclear as to what variation of $\alpha$ between two values of $l_{max}$ would represent convergence as $\alpha$ 
%itself is a dynamically varying quantity, see figure \ref{fig:alphavar}.

@@

\begin{table}
\begin{center}
\begin{tabular}{ccccc}
\multicolumn{5}{c}{$Q$, Fourier Amplitudes, and $\alpha$}\\ \hline\hline
$l_{max}$ & $Q_{avg}$   & $\langle A_{tot} \rangle$   & $\langle A_{2-7} \rangle / \langle A_{tot} \rangle$ & $\alpha_{avg}$ \\\hline
64   & 1.26 & 1.96 &  0.76 & 0.069 \\
128 & 1.24 & 1.91 &  0.62 & 0.044 \\
256 & 1.39 & 1.83 &  0.54 & 0.026 \\
512 & 1.48 & 1.95 &  0.49 & 0.020 \\ 
$\infty$ & & &0.43 & 0.017 \\ \hline
\label{tbl:ams}
\end{tabular}
\caption{ All quantities are time-averaged over 12 -- 18 ORP.
$Q_{avg}$ and $\alpha_{avg}$ are also spatially
averaged over 10 -- 40 AU.  The entries for ``$\infty$'' are based on Richardson extrapolation,
as explained in the text.}  
\end{center}
\end{table}

@@

\begin{figure}
\plotone{Figure1.eps}
\caption{Azimuthally averaged mid-plane Toomre Q distribution versus radius for each of the four resolutions at t $\sim$ 18 ORPs}
\label{fig:Final_Q}
\end{figure}

\begin{figure}
\plotone{Figure2.eps}
\caption
{
Mid-plane disk densities at $t \sim 18$ ORPs for simulations with 64, 128, 256 and 512 azimuthal grid elements.
The simulations differ only in the number of  azimuthal zones used in the calculations.  Densities out of the plane, along an azimuthal cut through the disk, are displayed below the face-on views.  The color scale is logarithmic, and axis units are AU. 
}
\label{fig:DensityPlots}
\end{figure}
\newpage

@@

\begin{figure}
\plotone{Figure6.eps}
\caption
{Effective $\alpha$'s for the $t_{cool} =$ 2 ORP, $\gamma = 5/3$, $\Sigma \sim r^{ -1}$ disk, averaged between 12 and 18
  ORPs, for four different azimuthal grid resolutions, given by the number of azimuthal grid-points $l_{max}$. The
  dashed lines show the $\alpha$ from equation (\ref{eq:gammie}) (upper: strongly self-gravitating limit, lower:
  non-self-gravitating limit), while the dotted line at $\log(\alpha) = -1.22$ represents the maximum stress a disk can
  maintain without fragmenting according to \citet{rice2005}. 
}
\label{fig:alpha_v_radius}
\end{figure}
\newpage

>>>>

The initially unstable disk model passed through several phases of evolution \citep[see also][]{pickett2003, mejia2005}.  
During the initial axisymmetric phase, 
which lasts several ORP, the disk cools and contracts.  The contraction is small radially but dramatic in the vertical direction. Around 3 to 4 ORP, the instabilities begin to grow to nonlinear amplitudes, and the disk 
then undergoes a strong burst of GIs that predominantly manifest themselves in a few discrete global spiral modes.  The disk expands violently during the burst phase, producing a significant rearrangement of the disk's mass distribution on a timescale of a few ORP. This is then followed by a period of several ORP where heating temporarily washes out some of the non-axisymmetry in the disk.  Finally, following this transition phase, the disk settles into a quasi-steady, long-lived asymptotic 
phase of sustained GI-activity over a large part of the disk, with an overall balance of heating and cooling.

Simulations were run with four different angular resolutions, with grid sizes in cylindrical coordinates $(r,\phi,z)$ of  $(j_{max}, k_{max}, l_{max}) =$ (512,64,64), (512,64,128), (512,64,256), and (512,64,512). 
For reference, the radius $r = 33$ AU at which the ORP is defined is at radial cell $j = 200$.  The radial grid extends to 512
to accomodate disk expansion during outburst.
Because of the computational overhead associated with running each simulation starting from $t = 0$, the $l_{max} =$ 128 simulation was run through the axisymmetric, burst and transition phases. Simulations using $l_{max} =$ 64, 256, and 512 all begin by a linear interpolation of the $l_{max} =$ 128 simulation to higher or lower azimuthal resolution at 9.6 ORP, near the end of the transition
phase. Although this strategy saves a large amount of computational time, it limits the scope of the analysis to the asymptotic phase. By 12 ORP, all four disks appear to have transitioned to the asymptotic state,
e.g., they all display roughly steady $Q(r)$ profiles starting at $\sim 12$ ORP.  All simulations were 
run through $\sim 18$ ORP.

@@

Figure \ref{fig:DensityPlots}, shows mid-plane and radial densities  at $t \sim 18$ ORP for the $l_{max} =$ 64, 128, 256, and 512 simulations. It is readily apparent that the character of the non-axisymmetric density structures differ with 
resolution. One can clearly see that the lower resolution simulations, i.e., $l_{max} = 64$ and 128, have primarily low-order structures with $m = 2$ and 3 dominating. In contrast, the higher resolution simulations have much more fine structure, 
and the low-order $m$-values no longer dominate.  
The lower resolution (smaller $l_{max}$) simulations display longer wavelength spiral structures, with larger amplitudes and more coherence than those seen in higher resolution simulations. Higher angular resolution allows non-axisymmetric structures to grow in higher-order azimuthal $m$-values, as demonstrated by a Fourier decomposition of the density. The strengths of these components are given by their global Fourier amplitudes,

\begin{equation}
A_m = \frac{(a_m^2 + b_m^2)^{1/2}}{\pi\int\rho_o \varpi {\rm d}\varpi {\rm d}z},
\end{equation}
where
\begin{subequations}
\begin{align}
a_m &= \int \rho \cos(m\phi)\varpi {\rm d}\varpi {\rm d}z {\rm d}\phi,\\
b_m &=\int \rho \sin(m\phi)\varpi {\rm d}\varpi {\rm d}z {\rm d}\phi.
\end{align}
\end{subequations}
Here  $\rho_o$ is the axisymmetric component of the density. In what follows, $A_m$ is averaged over time to suppress fluctuations on the dynamic timescale due to the chaotic nature of GIs in the asymptotic  phase.
In particular, $\langle A_{tot} \rangle$ will represent the power over the radial range 10 -- 40 AU, summed from $ m = 2$ to $l_{max}/2$ and averaged over the time range 12 -- 18 ORP. The Fourier amplitudes cannot be measured at resolutions smaller than $l_{max}/2$, therefore $A_m$ is limited to modes $m \le l_{max}/2$.  
Because the central star is artificially fixed to the grid center, the $m=1$ mode may not
be accurately treated. For this reason, it is excluded from $\langle A_{tot} \rangle$.  As discussed below in \S3.2,
we expect this exclusion to have minimal impact on the results of this work.

@@

The gravitational stresses of equation \eqref{alpha1} can be evaluated using the gravitational torque of equation \eqref{torque1}, i.e.,
\begin{equation}
\label{newtonstress}
\begin{split}
 T_{\varpi\phi}^{grav}\left( \varpi \right) & = \frac{1}{2\pi\varpi^2}C_Z\\
                                & = - \frac{1}{2\pi\varpi^2} \int \rho\frac{\partial\Phi}{\partial\phi} {\rm d}V.
\end{split}
\end{equation}
Figure \ref{fig:alpha_v_radius} shows $\alpha_{\rm{eff}}$, time-averaged from 12 to 18 ORP, calculated using equations \eqref{alpha1} and \eqref{newtonstress},
for the four grid resolutions.  For comparison, 
$\alpha_{\rm{eff}}$ predicted by equation \eqref{eq:gammie} from \citet{gammie2001} are plotted for disks.  The lower  Gammie curve applies for the strongly self-gravitating limit while the upper curve 
represents the non-self-gravitating limit.   The $l_{max} = 512$ curve is consistent with these two limits.  However, 
the  $l_{max} = 512$ curve does not represent a converged model.
To determine whether the converged value of $\alpha_{\rm{eff}}$ is consistent with predictions, we examine 
the spatially (10 -- 40 AU) and temporally (12 -- 18 ORP) averaged  $\alpha_{avg}$,
provided in table 1, for each value of  $l_{max}$. A Richardson extrapolation applied to these values  
converges to $\alpha_{avg} = 0.017$ (over the same radial  and time range)
as the grid spacing goes to zero.   This falls
between the $\alpha_{avg}$ values for the Gammie curves 0.014 (strongly self-gravitating) and 0.027 (non-self-gravitating).

@@

The results above permit an assessment of appropriate azimuthal grids for the
problem under consideration and similar problems. The $l_{max} = 512$ simulation yields a value 
for $\alpha_{avg}$ of 0.020. This overestimates the extrapolated converged value of $\alpha_{avg}
= 0.017$ by $\sim 18$\%. The $l_{max} = 512$ simulation also overestimates the fractional
power in the high-order ($m = 2$ -- 7) modes by essentially the same percentage. However, it should be noted that the fractional difference between successive doubling of the resolution has decreased for $l_{max} = 512$. From $l_{max} =64$ to 128 the fractional difference in $\alpha_{avg}$ is 36\%. This decreases to 26\% for the jump from $l_{max} = 256$ to 512. Furthermore, the converged value represents infinite azimuthal resolution, which is, of course, impossible to achieve in a fixed grid scheme. 
%It is unclear as to what variation of $\alpha$ between two values of $l_{max}$ would represent convergence as $\alpha$ 
%itself is a dynamically varying quantity, see figure \ref{fig:alphavar}. 
In addition to the convergence of $\alpha_{avg}$, table \ref{tbl:ams} shows the convergence of the $\dot{M}$
from 10 -- 40 AU averaged from 12 to 18 ORP. The $\dot{M}_{avg}$ measurement shows convergence similar to that
of the $\alpha_{avg}$ measurement.

@@

\begin{table}
\begin{center}
\begin{tabular}{cccccc}
\multicolumn{5}{c}{$Q$, Fourier Amplitudes, and $\alpha$}\\ \hline\hline
$l_{max}$ & $Q_{avg}$   & $\langle A_{tot} \rangle$   & $\langle A_{2-7} \rangle / \langle A_{tot} \rangle$ &
$\alpha_{avg}$ & $\dot{M}_{avg} ~\mathrm{M_\odot/yr}$\\\hline
64   & 1.26 & 1.96 &  0.76 & 0.069 & 8.9$ \times 10^{-7}$ \\
128 & 1.24 & 1.91 &  0.62 & 0.044 & 3.7$ \times 10^{-7}$ \\
256 & 1.39 & 1.83 &  0.54 & 0.026 & 2.5$ \times 10^{-7}$ \\
512 & 1.48 & 1.95 &  0.49 & 0.020 & 2.4$ \times 10^{-7}$ \\ 
$\infty$ & & &0.43 & 0.017 & \\ \hline
\label{tbl:ams}
\end{tabular}
\caption{ All quantities are time-averaged over 12 -- 18 ORP.
$Q_{avg}$, $\alpha_{avg}$, and $\dot{M}_{avg}$  are also spatially
averaged over 10 -- 40 AU.  The entries for ``$\infty$'' are based on Richardson extrapolation,
as explained in the text.}  
\end{center}
\end{table}

@@

\begin{figure}
\plotone{Figure1.eps}
\caption{Azimuthally averaged mid-plane Toomre Q distribution versus radius for each of the four resolutions at t $\sim$ 18 ORP}
\label{fig:Final_Q}
\end{figure}

\begin{figure}
\plotone{Figure2.eps}
\caption
{
Mid-plane disk densities at $t \sim 18$ ORP for simulations with 64, 128, 256 and 512 azimuthal grid elements.
The simulations differ only in the number of  azimuthal zones used in the calculations.  Densities out of the plane, along an azimuthal cut through the disk, are displayed below the face-on views.  The color scale is logarithmic, and axis units are AU. 
}
\label{fig:DensityPlots}
\end{figure}
\newpage

@@

\begin{figure}
\plotone{Figure6.eps}
\caption
{Effective $\alpha$'s for the $t_{cool} =$ 2 ORP, $\gamma = 5/3$, $\Sigma \sim r^{ -1}$ disk, averaged between 12 and 18
  ORP, for four different azimuthal grid resolutions, given by the number of azimuthal grid-points $l_{max}$. The
  dashed lines show the $\alpha$ from equation (\ref{eq:gammie}) (upper: strongly self-gravitating limit, lower:
  non-self-gravitating limit), while the dotted line at $\log(\alpha) = -1.22$ represents the maximum stress a disk can
  maintain without fragmenting according to \citet{rice2005}. 
}
\label{fig:alpha_v_radius}
\end{figure}
\newpage
